---
title: "Statistics_Task"
author: "Oluwakemisola"
date: "4/26/2021"
output: html_document
---

Question 1
```{r}
getwd()
Data1 <- read.csv("lbw.csv", header = TRUE)
mean(Data1$bwt)
median(Data1$bwt)
```
Question 2
Hypothesis testing is a formal procedure for investigating our ideas about the world using statistics. 
There are 5 main steps in hypothesis testing:
1. State your research hypothesis as a null (Ho) and alternate (Ha) hypothesis.
2. Collect data in a way designed to test the hypothesis.
3. Perform an appropriate statistical test.
4. Decide whether the null hypothesis is supported or refuted.
5. Present the findings in your results and discussion section.

Question 3: Hypothesis testing
```{r}
```


```{r}
#1. Total births were to mothers that were smokers
Data1$smoke
sum(Data1$smoke==1)/nrow(Data1)

names <- Data1%>%
select(smoke)%>%
filter(smoke==1)
names
length(names)
dim(names)
dim(Data1)
prop.test(74, 189, 0.5)

```
```{r}
#2. total births was of babies that were classified as low birth weight
Data1$low
sum(Data1$low==1)/nrow(Data1)

names <- Data1%>%
select(low) %>%
filter(low==1)
names
length(names)
dim(names)
dim(Data1)
prop.test(59, 189, 0.5)

```
3.	Make a contingency table of low birth weight vs. smoke
```{r}
low<-Data1$low
smoke<-Data1$smoke
table(smoke)
table(low)
table(low, smoke)

```
4.	Conduct a hypothesis test to answer the following question: 
```{r}
chisq.test(low, smoke)
#smokers and non smokers give birth the same low-birth weight children... Reject Null hypothesis....
```
5.	To investigate the difference between the average weights of hypertensive mothers
```{r}
Data1
#Null hypothesis: No difference in the average weight of hypertensive mothers and non hypertensive mothers.
#Alternative: there is a difference between the average weight of hypertensive mothers and non hypertensive mothers.
boxplot(Data1$bwt~low, data=Data1)
aov(Data1$bwt~ht, data=Data1)
x<-aov(Data1$bwt~ht, data=Data1)
summary(x)
#Reject Null hypothesis
```


question 3
```{r}
a<-c(32.2, 37.5, 41.7, 53.8, 50.2, 48.2, 46.3, 65.0, 44.8)
a
mean(a)
median (a)
#If the person 65.0 years of age retires and is replaced on the faculty with a person 46.5 years old. what is the new mean age? 
b<-c(32.2, 37.5, 41.7, 53.8, 50.2, 48.2, 46.3, 46.5, 44.8)
b
mean(b)
median(b)

```

